%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,10pt]{article} % Default font size and paper size

\usepackage{fontspec} % For loading fonts
\usepackage{cmbright} % Font package
\defaultfontfeatures{Mapping=tex-text}

\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

%\usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be \usepackage{fullpage}
\usepackage[margin=0.5in]{geometry}

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections

\usepackage{longtable} % From http://tex.stackexchange.com/questions/131601/how-shift-a-part-of-the-long-table-to-the-next-page-in-latex

\begin{document}

\pagestyle{empty} % Removes page numbering

\font\fb=''[cmr10]'' % Change the font of the \LaTeX command under the skills section

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\par{\centering{\Huge Daniel Murphy}\bigskip\par} % Your name

\section{Personal Info}

\begin{tabular}{rl}
Location: & Nottingham \\
\textsc{Phone:} & 07895 999209\\
\textsc{Email:} & \href{mailto:danhatesnumbers@gmail.com}{danhatesnumbers@gmail.com}
\end{tabular}

%----------------------------------------------------------------------------------------
%	PERSONAL STATEMENT	
%----------------------------------------------------------------------------------------

\section{Personal Statement}
As a final year student at Nottingham Trent University who is on track for a 1st class honours degree
in Computer Science, I have undertaken a one year industrial placement with ARM as a Software
Engineer. This placement has allowed me to strengthen my existing technical skills and build new
ones to solve the challenges I was presented with. I find technical problems to be an enjoyable
challenge and see them as an opportunity to learn something new. \\
My eventual career ambition is to work my way into a technical lead role, becoming an expert in the
field I eventually find myself in, allowing me to impart knowledge to my colleagues and help them
develop as engineers.

%----------------------------------------------------------------------------------------
%	Technical Skills
%----------------------------------------------------------------------------------------

\section{Technical Skills}

\begin{tabular}{l|l|l|l}
\textit{Languages} & \textit{Frameworks} & \textit{Software} & \textit{Operating Systems} \\
C\# & WPF & Visual Studio & Windows \\
Python & ASP.NET MVC \& Web API & Git & Arch Linux \\
Javascript & jQuery & VirtualBox & \\
C++ & Xamarin Mobile & VMWare Workstation \& ESXi & \\
Java & Android SDK & & \\
SQL & Flask & & \\
\end{tabular}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE 
%----------------------------------------------------------------------------------------

\section{Work Experience}

\begin{longtable}{r|p{16cm}}

\emph{August 2018} & \textbf{Information Security Consultant} at Capital One, Nottingham \\
to & \\
Current & INSERT JOB DESC HERE \\
\multicolumn{2}{c}{} \\

\emph{November 2016} & \textbf{Quality Engineer} at Capital One, Nottingham \\
to & \\
August 2018 & INSERT JOB DESC HERE \\
\multicolumn{2}{c}{} \\

\emph{May 2014} & \textbf{Graduate Software Engineer} at Gala Coral Group, Nottingham \\
to & \\
November 2016 & My role at Gala provided me with an excellent opportunity to work with the Xamarin cross-platform C\# mobile app development framework, building new functionality and resolving technical debt in a suite of line of business iOS apps. I was responsible for moving to a virtualised OS X build infrastructure, using a Mac Mini running VMWare ESXi to provide each developer on the team with their own build host. I have also implemented Continuous Integration builds for a number of existing projects (including mobile apps, web apps and a WPF app) using TeamCity. As part of
this process of setting up Continuous Integration, I developed a tool that leverages the Swagger API documentation project and the AutoRest program from the Azure team to generate, build and package Portable Class Library compatible API clients from a JSON representation of the API. \\
\multicolumn{2}{c}{} \\

\emph{June 2012} & \textbf{Software Engineer Industrial Placement} at ARM, Cambridge \\
to & \\
August 2013 & While working at ARM, I was part of a team of engineers embedded in the Marketing Communications department. The majority of my time was spent building technical demonstrations of ARM technologies to showcase a set of marketing requirements. I also staffed demo booths at events that ARM attended, explaining to partners and members of the public what the demonstrations were doing, how they were built and answering any questions they may have. \\
\multicolumn{2}{c}{} \\

\emph{October 2011} & \textbf{Student Ambassador \& Mentor} at Nottingham Trent University \\
to & \\
June 2012 & My responsibilities in this position included running Drop-In sessions to support other Computing students with work they were finding problematic, representing the University at Open Events and answering any questions prospective students had about University and the Computer Science Department. I also assisted a senior lecturer in delivering first year programming labs. I was invited to take on this role by the University based on my first year grades. \\

\end{longtable}
\pagebreak
\section{Projects}
\textbf{Social Event Planning Web App for the Elderly} \\
During the final year of my degree, I built a web application to assist Social Event organisation in Sheltered Accomodation and Care homes for my Advanced Analysis \& Design group coursework. It was developed using the ASP.NET stack with jQuery and the Twitter Bootstrap Frameworks. I was primarily involved with the development of the Business Logic and User Interface and this gave me an opportunity to learn the MVC design pattern and strengthen my skills in User Interface design. \\
\par

\textbf{C++11 Thread Pool for Parallel Data Processing} \\
As part of one of my final year degree modules, Advanced Software Engineering, I conducted an investigation into the C++11 Threading library and built a small library for managing a pool of Threads for processing large datasets in parallel. This library included a Concurrency-Safe version of the STL Queue container and constructed a task queue using Lambdas to produce closures that wrapped method calls with the object they were being called on. \\
\par

\textbf{Highly Concurrent Compute Demo} \\
During my Industrial Placement at ARM, the main project I was responsible for was building a demonstration of highly concurrent computation on a server platform, initially as a wrapper around an existing piece of software to work in a distributed environment. This evolved to building internal instrumentation of the wrapper, data processing tools for the instrumentation data and a visualisation of the current computation task on Android which was later rebuilt as a web page that updated dynamically. \\
\par

\textbf{Android Single Device Computing Demo} \\
Another project I was responsible for while on my Industrial Placement at ARM was to build a demonstration of where ARM believe the future of computing lies. I worte an Android application to detect the state of the Dock connector on a Samsung Galaxy S4 and alter the layout and target DPI of various applications on the phone to provide a better experience when connected to an external screen. \\
\par

\section{Education}
\begin{tabular}{r|ll}
Sept 2010 -& Nottingham Trent University & \\
May 2014& \textbf{BSc Computer Science} & 1st Class (Hons) \\
\end{tabular} \\
\begin{tabular}{r|l}
Sept 2009 -& City College, Norwich \\
Jun 2010 & \textbf{AS Levels: }Photography (D), Psychology (D) \\
\multicolumn{2}{c}{} \\
Sept 2007 -& The Hewett Sixth Form, Norwich \\
Jun 2009 & \textbf{BTEC National Award: }Information Technology (Distinction) \\
& \textbf{A Levels: }Maths (D), Chemistry (D) \\
\multicolumn{2}{c}{} \\
Sept 2005 -& The Hewett School, Norwich \\
Jun 2007 & \textbf{GCSEs: }10 Grades A - C including Maths \& English \\
\end{tabular}
\end{document}
